Hou10ni

### 2017-06-28 hou10ni/Tutorial/hou10ni_profile.tex
Hou10ni's kernel : Add OpenMP

\title{Hou10ni Profiling with TAU}
\date{}

@@

This document presents some results obtained with the performance evaluation tool TAU on the application hou10ni.

@@

\section{Trace Analysis with Lucas and Arnaud's tool}

>>>>

\title{Hou10ni}
\date{}

@@

This document presents a study of hou10ni's kernel. We present results obtained with the performance evaluation tools TAU and Paje on the application.

\tableofcontents

\newpage

\section{Build and launch hou10ni}

Compilation:
\begin{cverbatim}
mkdir build && cd build
cmake ..
ccmake ..
make
cd .. 
\end{cverbatim}

\noindent Execution with 4 MPI processes:
\begin{cverbatim}
mpirun -np 4 build/hou10ni.out < HPC4E.dat
\end{cverbatim}

@@

\section{Trace Analysis with PAJE}
